On $K_2$-analogue of Serre problem for $\SL_4$

### 2018-08-28 paper.tex
Written down claims

\begin{lemma}
 For $\xi \in B_d$, $d\leq m+1$, $\eta \in B_{m+1}$ and $\alpha, \alpha' \in \Phi$ such that $\alpha + \alpha'\not\in\Phi\cup\{0\}$
 the following relation holds in $G_m$:
  \begin{equation} \label{eq:verify-bmp2} [S_\alpha(\xi), S_{\alpha'}(\eta)] = 1. \end{equation}
\end{lemma}
\begin{proof}
Write $\eta = bt^{m+1}$ for some $b\in A$.
\begin{enumerate}
\item \label{case:1} First consider the case $d \leq 0$. There are two further subcases.
 \begin{enumerate}
  \item \label{case:1a} Case $\alpha \not \perp \alpha'$. 
  Without loss of generality we may assume that $\alpha' = \alpha + \beta$
  for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
  Using~\eqref{eq:H1iii} and~\eqref{eq:bm} we obtain
   \begin{multline} \nonumber
   [S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] = \\   
  = [[x_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] = 1 \text{ for some $b'\in A$ }.
  \end{multline}
  What this really proves: $PERP(d, 1)$ and $NONPERP(d, m)$ imply $NONPERP(d, m+1)$.
  \item Case $\alpha \perp \alpha'$. 
  As before, we set $\alpha' = \gamma$ and use~\eqref{eq:H1iii},\eqref{eq:bm} and~\eqref{eq:cm}:
  \begin{multline} \nonumber
   [S_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [S_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] = \\   
  = [[S_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] = 1.
  \end{multline}
 \end{enumerate}

>>>>

\begin{lemma}
 For $\xi \in B_d$, $d\leq m+1$, $\eta \in B_{m+1}$ and $\alpha, \alpha' \in \Phi$ such that $\alpha + \alpha'\not\in\Phi\cup\{0\}$
 the following relation holds in $G_m$:
  \begin{equation} \label{eq:verify-bmp2} [S_\alpha(\xi), S_{\alpha'}(\eta)] = 1. \end{equation}
\end{lemma}
\begin{proof}
We can assume that $\eta = bt^{m+1}$ for some $b\in A$.

Claim 1: $\perp(d, 1)$ and $\angle(d, m)$ imply $\angle(d, m+1)$.
\begin{align*}
[S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [S_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]]
 & \text{ by~\eqref{item:i} and~\eqref{eq:defmpn}}\\
 = [[S_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)]
 & \text{ by~$\perp(d, 1)$}\\
 = 1
 & \text{ by~$\angle(d, m)$.} \end{align*}

Claim 2: $\perp(d, 1)$ and $\angle(d, m)$ imply $\angle(d, m+1)$.
 \begin{align*}
[S_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [S_\alpha(\xi), [x_{\beta+\gamma}(t), x_{-\beta}(b't^m)]]
 & \text{ by~\eqref{item:i} and~\eqref{eq:defmpn}}\\
 = [[S_\alpha(t^d), x_{\alpha+\beta+\gamma}(t)], {}^{x_{\alpha+\beta+\gamma}(t)}\!x_{-\gamma}(b't^m)]
 & \text{ by~$\perp(d, 1)$}\\
 = 1
 & \text{ by~$\angle(d, m)$.} \end{align*}

Claim 2: (first line of equalities proves nothing for $d=0$)
\begin{align*}
{}^{S_\gamma(t^d)}S_\alpha(bt^{m+1}) = {}^{S_\gamma(t^d)}[S_{-\beta}(b't^{m+1}), x_{\alpha+\beta}(1)] 
& \text{ by~\cref{lem:bmp1}}\\
 = [S_{-\beta}(b't^{m+1}), {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]                                     
 & \text{ by $\angle(d, m+1)$}\\
 = [[x_{-\beta-\gamma}(b''t^{m+1-d}), S_\gamma(t^d)], {}^{S_\gamma(t^d)}x_{\alpha+\beta}(1)]          
 & \text{ by~\eqref{eq:verify-bmp1'}}\\
 = [x_{-\beta-\gamma}(b''t^{m+1-d)}), [S_\gamma(t^d), x_{\alpha+\beta}(1)]]                           
 & \text{ by~\eqref{eq:H1iii} and~$\perp(m+1-d, 0)$}\\
 = S_{\alpha}(b'''t^{m+1})                                                                            
 & \text{ by~\eqref{eq:verify-bmp1'}} \end{align*}

\begin{align*}
 S_{\alpha+\beta+\gamma}(abt^{m+1}) = {}^{S_{-\beta}(t^d)}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) 
 & \text{ by previous line}\\
 = {}^{S_{-\beta}(t^d)}\![x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
 & \text{ by~\eqref{eq:verify-bmp1'}} \\
 = [S_{\alpha}(b't^{m+1}) x_{\alpha+\beta}(b't^{m+1-d}), S_\gamma(at^d)] 
 & \text{ by~\eqref{eq:verify-bmp1'} and $\angle(d, m+1)$ }\\
 = {}^{S_{\alpha}(b't^{m+1})}\!S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
 & \text{ by~\eqref{eq:H1ii} and~\eqref{eq:verify-bmp1'}} \\
 = S_{\alpha+\beta+\gamma}(abt^{m+1}) [S_{\alpha}(b't^{m+1}), S_\gamma(at^d)] 
 & \text{ by $\angle(m+1, m+1)$,}
\end{align*}

\begin{enumerate}
\item \label{case:1} First consider the case $d \leq 0$. There are two further subcases.
 \begin{enumerate}
  \item \label{case:1a} Case $\alpha \not \perp \alpha'$. 
  Without loss of generality we may assume that $\alpha' = \alpha + \beta$
  for some $\rA_3$-triple $(\alpha, \beta, \gamma)$.
  Using~\eqref{eq:H1iii} and~\eqref{eq:bm} we obtain
   \begin{multline} \nonumber
   [S_\alpha(\xi), S_{\alpha+\beta}(bt^{m+1})] = [x_\alpha(\xi), [x_{\alpha+\beta+\gamma}(b't^m), x_{-\gamma}(t)]] = \\   
  = [[x_\alpha(\xi), x_{\alpha+\beta+\gamma}(b't^m)], {}^{x_{\alpha+\beta+\gamma}(b't^m)}\!x_{-\gamma}(t)] = 1 \text{ for some $b'\in A$ }.
  \end{multline}
  What this really proves: $PERP(d, 1)$ and $NONPERP(d, m)$ imply $NONPERP(d, m+1)$.
  \item Case $\alpha \perp \alpha'$. 
  As before, we set $\alpha' = \gamma$ and use~\eqref{eq:H1iii},\eqref{eq:bm} and~\eqref{eq:cm}:
  \begin{multline} \nonumber
   [S_\alpha(\xi), S_{\gamma}(bt^{m+1})] = [S_\alpha(\xi), [x_{\beta+\gamma}(b't^m), x_{-\beta}(t)]] = \\   
  = [[S_\alpha(\xi), x_{\beta+\gamma}(b't^m)], {}^{x_{\beta+\gamma}(b't^m)}\!x_{-\beta}(t)] = {}^{x_{\beta+\gamma}(b't^m)}\![x_{\alpha+\beta+\gamma}(b't^m\xi), x_{-\beta}(t)] = 1.
  \end{multline}
 \end{enumerate}
